Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-06-29 figures.Rmd
updated figures

@@

library(tidyverse)
library(janitor)
library(FSA)
library(factoextra)
library(ggrepel)
library(ggpubr)
library(tidymodels)
library(vip)
library(scales)
library(reshape)

@@

@@

                "Deoxy Hb" = "cerebral.hbdeox", "Deoxy Hb α" = "cerebral.hbdeox.alpha", 
                "Oxy Hb" = "cerebral.hbox", "Oxy Hb α" = "cerebral.hbox.alpha",  
                "HbO2%" = "cerebral.sat", "HbO2% α" = "cerebral.sat.alpha", 
                "[HbT]" = "cerebral.thc", "[HbT]α" = "cerebral.thc.alpha")

@@

df_hbox_voi <- df_hbox_impute %>% 
  dplyr::select(c(Status, `Oxy Hb`, `Oxy Hb α`, `Deoxy Hb`, `Deoxy Hb α`, `HbO2%`, `HbO2% α`, `[HbT]`, `[HbT]α`)) %>% 
  dplyr::filter(`Deoxy Hb α` < 3)

df_hbox_voi_long <- df_hbox_voi %>% 
  pivot_longer(2:9, names_to = "variable", values_to = "value") %>%
  mutate(variable = factor(variable, levels = c("Oxy Hb", "Oxy Hb α",   
                                                 "Deoxy Hb", "Deoxy Hb α", 
                                                "HbO2%", "HbO2% α", 
                                                "[HbT]", "[HbT]α")))

@@

df_hbox_voi_long %>% dplyr::filter(variable %in% c("Oxy Hb", "Deoxy Hb", "HbO2%", "[HbT]")) %>%

@@

  theme(strip.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15))

@@

df_hbox_voi_long %>% dplyr::filter(variable %in% c("Oxy Hb α", "Deoxy Hb α", "HbO2% α", "[HbT]α")) %>%

@@

  theme(strip.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        legend.position = "none")

@@

  theme_bw() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20))

@@

  theme_bw() +
  theme(axis.title = element_text(size = 25),
        axis.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15))

@@

# create df of potential regressors
df_hbox_reg <- df_hbox_impute %>% 
  dplyr::select(c(Status, `Hematocrit (%)`, `Lactate (mmol/L)`, `Oxy Hb`, `Oxy Hb α`, `Deoxy Hb`, `Deoxy Hb α`, `HbO2%`, `HbO2% α`, `[HbT]`, `[HbT]α`)) %>% 
  dplyr::filter(`Deoxy Hb α` < 3)

@@

    mutate_if(is.factor, factor, levels = c("Lactate (mmol/L)", "Hematocrit (%)", "Oxy Hb", "Deoxy Hb", "HbO2%", "[HbT]", "Oxy Hb α", "Deoxy Hb α", "HbO2% α", "[HbT]α")) %>%

@@

    xlab("") +
    ylab("") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 0.9),
          axis.text = element_text(size = 35),
          legend.text = element_text(size = 40),
          legend.title = element_text(size = 50),
          legend.key.size = unit(2, 'cm'),
          plot.title = element_text(size = 30)
    )

@@

# pivot longer and change factor levels
df_hbox_reg_long <- df_hbox_reg %>% 
  pivot_longer(2:11, names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = c("Lactate (mmol/L)", "Hematocrit (%)", "Oxy Hb", "Oxy Hb α", "Deoxy Hb", "Deoxy Hb α", "HbO2%", "HbO2% α" ,"[HbT]", "[HbT]α")))

@@

  theme_bw() +
  theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20),
        strip.text = element_text(size = 20))

>>>>

<style type="text/css">
  body{
  font-family: Arial;
  font-size: 12pt;
}
</style>

@@

library(tidyverse)
library(janitor)
library(FSA)
library(factoextra)
library(ggrepel)
library(ggpubr)
library(tidymodels)
library(vip)
library(scales)
library(reshape)
library(extrafont)
library(grDevices)

@@

font_import()

@@

                "[Hb]" = "cerebral.hbdeox", "[Hb]α" = "cerebral.hbdeox.alpha", 
                "[HbO2]" = "cerebral.hbox", "[HbO2]α" = "cerebral.hbox.alpha",  
                "HbO2%" = "cerebral.sat", "HbO2% α" = "cerebral.sat.alpha", 
                "[HbT]" = "cerebral.thc", "[HbT]α" = "cerebral.thc.alpha")

@@

df_hbox_voi <- df_hbox_impute %>% 
  dplyr::select(c(Status, `[HbO2]`, `[HbO2]α`, `[Hb]`, `[Hb]α`, `HbO2%`, `HbO2% α`, `[HbT]`, `[HbT]α`)) %>% 
  dplyr::filter(`[Hb]α` < 3)

df_hbox_voi_long <- df_hbox_voi %>% 
  pivot_longer(2:9, names_to = "variable", values_to = "value") %>%
  mutate(variable = factor(variable, levels = c("[HbO2]", "[HbO2]α",   
                                                 "[Hb]", "[Hb]α", 
                                                "HbO2%", "HbO2% α", 
                                                "[HbT]", "[HbT]α")))

@@

df_hbox_voi_long %>% dplyr::filter(variable %in% c("[HbO2]", "[Hb]", "HbO2%", "[HbT]")) %>%

@@

  theme(text = element_text(family = "Arial"),
        strip.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15))

@@

df_hbox_voi_long %>% dplyr::filter(variable %in% c("[HbO2]α", "[Hb]α", "HbO2% α", "[HbT]α")) %>%

@@

  theme(text = element_text(family = "Arial"),
        strip.text = element_text(size = 15),
        axis.title = element_text(size = 15),
        axis.title.y = element_blank(),
        axis.text = element_text(size = 15),
        legend.position = "none")

@@

  theme_bw() +
  theme(text = element_text(family = "Arial"),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20))

@@

  theme_bw() +
  theme(text = element_text(family = "Arial"),
        axis.title = element_text(size = 25),
        axis.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 15))

@@

# create df of potential regressors
df_hbox_reg <- df_hbox_impute %>% 
  dplyr::select(c(Status, `Hematocrit (%)`, `Lactate (mmol/L)`, `[HbO2]`, `[HbO2]α`, `[Hb]`, `[Hb]α`, `HbO2%`, `HbO2% α`, `[HbT]`, `[HbT]α`)) %>% 
  dplyr::filter(`[Hb]α` < 3)

@@

    mutate_if(is.factor, factor, levels = c("Lactate (mmol/L)", "Hematocrit (%)", "[HbO2]", "[Hb]", "HbO2%", "[HbT]", "[HbO2]α", "[Hb]α", "HbO2% α", "[HbT]α")) %>%

@@

    xlab("") +
    ylab("") +
    theme_bw() +
    theme(text = element_text(family = "Arial"),
          axis.text.x = element_text(angle = 45, hjust = 0.9),
          axis.text = element_text(size = 35),
          legend.text = element_text(size = 40),
          legend.title = element_text(size = 50),
          legend.key.size = unit(2, 'cm'),
          plot.title = element_text(size = 30)
    )

@@

# pivot longer and change factor levels
df_hbox_reg_long <- df_hbox_reg %>% 
  pivot_longer(2:11, names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = c("Lactate (mmol/L)", "Hematocrit (%)", "[HbO2]", "[HbO2]α", "[Hb]", "[Hb]α", "HbO2%", "HbO2% α" ,"[HbT]", "[HbT]α")))

@@

  theme_bw() +
  theme(text = element_text(family = "Arial"),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20),
        strip.text = element_text(size = 20))
